Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Deep Learning for CSI Feedback: One-Sided Model and Joint Multi-Module Learning Perspectives

@@

>>>>

Shehzad et al. \cite{shehzad2021design} proposes a novel machine learning-based approach for efficient Channel State Information (CSI) feedback in massive MIMO systems. The authors address the critical challenge of feedback overhead reduction while maintaining CSI accuracy, which is essential for realizing the full potential of massive MIMO technology. Their key innovation is a hybrid approach that combines conventional CSI feedback with twin recurrent neural network (RNN) predictors at both the base station (gNB) and user equipment (UE).

@@

	\bibitem{shehzad2021design} 
	M. K. Shehzad, L. Rose, S. Wesemann, M. Assaad, and S. A. Hassan, 
	``Design of an Efficient CSI Feedback Mechanism in Massive MIMO Systems: A Machine Learning Approach using Empirical Data,'' 
	arXiv preprint arXiv:2208.11951v1, 2021.
